\textls[-0]{\thetitle}

### 2023-03-14 metatheory2.tex
Attach universe level to MLTT.

Now we will need to attach syntax pieces with natural number indicating universe level. The explicit universe level $i$ now will attach to each context and type judgement $\goodCtx{\Gm}{i}$ and $\goodType{\Gm}{T}{i}$ basically indicating the context $\Gm$ and $T$ inhabits at what universe. Apparently, universe level will also attach to $\cU$. For two universe level $i,j$ (as natural number), we use $i \lcup j$ to denotes $\max(i,j)$.

>>>>

Now we will need to some attach syntax pieces with natural number indicating universe level. The explicit universe level $i$ now will attach to each context and type judgement $\goodCtx{\Gm}{i}$ and $\goodType{\Gm}{T}{i}$ basically indicating the context $\Gm$ and $T$ inhabits at what universe. Apparently, universe level will also be attached to $\cU$. For two universe level $i,j$ (as natural number), we use $i \lcup j$ to denotes $\max(i,j)$.

Since we work in an intrinsic-typed setting, some required premises can be omitted without ambiguity. For omitted context judgement $\goodCtx{\Gm}{k}$, the universe level is always $k$, hinted at the figure of judgement specification. Similar for type judgement $\goodType{\Gm}{T}{j}$.
